---
title: "Male/Female priorities -REDS data"
author: "Indira Tirumala"
date: "`r Sys.Date()`"
output: pdf_document
---

Goal: tabulate differences in ranking of issues between Gram Panchayats with women pradhan through reservation, versus GPs with open elections - for Rajasthan, UP and the rest of India. 
I.e. male/female priorities are not so different. 

Data used: REDS, SEPRI 2014-2016.

Following Manu's email, I would like to mention (in our conclusion) the possibility that male/female priorities are not so different.  So if you could tabulate the differences in Rajasthan, UP, and the rest of India, that would be helpful.  We'll stick that table in the SI, but I can refer to it in the text.  We'll want mean ratings for men and women, a column for the difference between the two, and a confidence interval around the difference.  I can use the latter to say that, although the N is small, the range of the confidence interval is still narrow enough to rule out markedly different priorities.


```{r, echo=FALSE} 

library(haven)
library(tidyverse)
library(rmarkdown)
library(knitr)
library(kableExtra)


```



```{r, echo=FALSE, warning=FALSE}

rm(list=ls())

# PHASE 1 

#Loading datasets 

setwd("C:/Users/indir/Dropbox/India Reservations/data/reds")

rankings1 = read_dta("./reds06/Sepri1/Village/SECTION_11_6.dta") 

stateinfo1 = read_dta("./reds06/Sepri1/Village/VILLAGE_DETAIL.dta")

reservations1 = read_dta("./reds06/Sepri1/Village/SECTION_11_D.dta")


#PHASE 2 

#Loading datasets 

rankings2 = read_dta("./reds06/Sepri2/Village/SECTION_11_6.dta") 

stateinfo2 = read_dta("./reds06/Sepri2/Village/VILLAGE_DETAIL.dta") %>%
     select(!q25_gps_n:q25_gps_e) %>%
     select(!q1_name_of_respondent:q2_designation)

reservations2 = read_dta("./reds06/Sepri2/Village/SECTION_11_D.dta")

#Appending 

rankings = rbind(rankings1, rankings2)

stateinfo = rbind(stateinfo1, stateinfo2)

reservations = rbind(reservations1, reservations2)

rm(rankings1, rankings2, stateinfo1, stateinfo2, reservations1, reservations2)


```



```{r, echo=FALSE, warning=FALSE}

#Preparing the datasets

#Reservations data: 

reservations= reservations %>%
  select(village_sr_no:s11_d1_p35_q07) %>%
  select(!s11_d1_p35_q03:s11_d1_p35_q06) %>%
  rename(panchayat_term = s11_d1_p35_q01) %>%
  rename(reservation_women = s11_d1_p35_q07) %>% 
  mutate(panchayat_term = recode(panchayat_term, 
                                 `1` = "current_gp", 
                                 `2` = "prev_gp")) %>%
     mutate(reserved_women = ifelse(reservation_women==1, "yes", "no")) %>%
     mutate(open_election = ifelse(reservation_women==1, "no", "yes")) %>%
     select(!reservation_women)
     


reservations %>% summarize(n_distinct(village_name))



#Rankings data 

rankings = rankings %>% 
     rename(issues = s11_6_p39_q01) %>%
     mutate(issues = recode(issues,
                            `1` = "drinking water supply", 
                            `2` = "sanitation, sewage",
                            `3` = "rural roads", 
                            `4` = "irrigation facilities", 
                            `5` = "transportation", 
                            `6` = "electrification",
                            `7` = "street lighting", 
                            `8` = "credit,subsidies for farmers", 
                            `9` = "communication facilites",
                            `10` = "school, education",
                            `11` = "health, nutrition facilities", 
                            `12` = "natural resource mgtm", 
                            `13` = "seasonal unemployment", 
                            `14` = "employment schemes"
                            )) %>%
     rename(current_gp = s11_6_p39_q03) %>%
     rename(prev_gp = s11_6_p39_q05) %>%
     select(!s11_6_p39_q04) %>%
     select(!s11_6_p39_q06) 

rankings = pivot_longer(rankings, cols=current_gp: prev_gp) %>%
     rename(rank = value) %>% 
     rename(panchayat_term = name)
     


#Stateinfo data 

stateinfo = stateinfo %>%
     select(!q1_2a_census_2001:q1_2b_census_2013) %>%
     select(!q1_1c:q1_1d) %>%
     rename(state = q1_1h)
     
stateinfo %>% summarize(n_distinct(village_name))

     
```



```{r}

#Merging the datasets 

final_data = inner_join(stateinfo, reservations, by = c("village_name", "gram_panchayat", "tehsil_taluka", "cd_block", "district"))

final_data = inner_join(final_data, rankings, by = c("village_name", "gram_panchayat", "tehsil_taluka", "cd_block", "district", "panchayat_term"))

final_data %>% summarize(n_distinct(village_name))

final_data %>% count(state)

final_data = final_data %>% mutate(state = recode(state, 
                      "TAAMIL NADU" = "TAMIL NADU", 
                      "TAMILNADU" = "TAMIL NADU",
                      "TAMILNDU" = "TAMIL NADU", 
                      "BALODA BAZAR" = "CHHATTISGARH",
                      "CHHATISGARH" = "CHHATTISGARH", 
                      "CHHTTISGARH" = "CHHATTISGARH", 
                      "HARIYANA" = "HARYANA", 
                      "MADHYA  PRADESH" = "MADHYA PRADESH",
                      "U.P" = "UTTAR PRADESH",
                      "GUJRAT" = "GUJARAT",
                      "MAHRASHTRA" = "MAHARASHTRA",
                      "ODISHA 15" = "ODISHA"
                      ))

final_data %>% count(state)


```





```{r}

#Creating the table 

table1 <- final_data %>%
  drop_na() %>%
  group_by(state, reserved_women, issues) %>%
  summarise(
    mean = mean(rank),
    sd = sd(rank), 
    n = n()
    ) %>%  
     pivot_wider(id_cols = c(state, issues), 
                      names_from = reserved_women, values_from = c(mean, sd, n)) %>%
     drop_na %>%
     rename(reserved_women = mean_yes, open_election= mean_no) %>%
     mutate(difference = round(reserved_women - open_election, 1)) %>%
    mutate(se_diff = sqrt((sd_yes^2 / n_yes) + (sd_no^2 / n_no)),
    ci_lower = difference - qt(0.975, df = pmin(n_yes, n_no) - 1) * se_diff,
    ci_upper = difference + qt(0.975, df = pmin(n_yes, n_no) - 1) * se_diff) %>% 
     mutate(ci_lower = round(ci_lower, 1), 
            ci_upper = round(ci_upper, 1)) %>%
     mutate(CI_95 = paste(ci_lower, ci_upper, sep = " , ")) %>% 
     select(!sd_yes:sd_no) %>%
     select(!se_diff:ci_upper) %>%
     mutate(reserved_women = round(reserved_women, 1), 
            open_election= round(open_election, 1)) %>%
     rename(n_reserved = n_yes) %>%
     rename(n_open = n_no) %>%
     ungroup(.) 

```


```{r}

#Creating table for Rajasthan only 

rajs_table = table1 %>%
     filter(., state=="RAJASTHAN") %>%
     mutate(Number_of_Villages = n_reserved + n_open) %>%
     rename(Issues = issues) %>%
     rename(Reserved_for_women = reserved_women) %>%
     rename(Open_election = open_election) %>%
     rename(Difference = difference) %>%
     rename(Confidence_Interval_95 = CI_95) %>%
     select(!c(state, n_reserved, n_open)) 

```



```{r, results='asis'}

#Generate tex file for the table for Rajasthan

sink("rajasthan_table.tex")

kable(rajs_table, format = "latex", booktabs = TRUE, caption = "Insert caption here") %>%
  cat()

sink()
```





